---
title: "Take-Home Exercise 2"
author: "Leonard Lee"
format:
  html:
    code-fold: true
    code-summary: "Show me the good stuff"
execute:
  warning: false
date: "18 May 2023"
date-modified: "`r Sys.Date()`"
---

Weight field calculating number of times target communicated with the source.

(multiple source to target links at diff times)

In and out weight (In degree and out degree)

Aggregate out big network

(In class ex reference to weight field)

```{r}
pacman::p_load(igraph, tidygraph, ggraph, 
               visNetwork, lubridate, clock,
               tidyverse, graphlayouts, jsonlite)


```

```{r}
MC2 <- fromJSON("data/mc2_challenge_graph.json")

```

```{r}
MC2_nodes <- as_tibble(MC2$nodes) %>%
  select(id,shpcountry, rcvcountry) #using select function to reorganise into desired order of columns

MC2_edges <- as_tibble(MC2$links) %>%
  select(source, target, valueofgoods_omu, valueofgoodsusd, weightkg, hscode, arrivaldate)

```

## Remove all duplicate rows

```{r}
MC2_edges <- MC2_edges %>% distinct()
MC2_nodes <- MC2_nodes %>% distinct()

```


```{r}
MC2_edges <- MC2_edges %>%
  mutate(Month = month(arrivaldate,
                        label = TRUE,
                        abbr = FALSE))

# rename columns
MC2_edges <- MC2_edges %>%
  rename('Source' = 'source', 
         'Target' = 'target', 
         'Value_OMU' = 'valueofgoods_omu', 
         'Value_USD' = 'valueofgoodsusd', 
         'Weight_KG' = 'weightkg', 
         'HS_Code' = 'hscode', 
         'Arrival_Date' = 'arrivaldate')

# rename columns
MC2_nodes <- MC2_nodes %>%
  rename('company' = 'id')
```

## Check for NA in from and to
```{r}
MC2_edges <- MC2_edges[complete.cases(MC2_edges[, c("Source", "Target")]), ]

```

```{r}
class(MC2_nodes$company)
MC2_nodes$company <- as.character(MC2_nodes$company)

```


```{r}
MC2_nodes <- transform(MC2_nodes, id = as.integer(factor(company, levels = unique(company))))


MC2_edges$Source <- MC2_nodes$id[match(MC2_edges$Source, MC2_nodes$company)]
MC2_edges$Target <- MC2_nodes$id[match(MC2_edges$Target, MC2_nodes$company)]


```

```{r}
MC2_nodes <- MC2_nodes %>%
  select(id, everything())

```

I have my link and nodes, create graph network (use biz network to make it interactive)

do the same for bundle, get a snap shot, then select the fishes that have interesting ones.
using HS code, can find out that a lot of rows are irrelevant (not related to fishing)

Alternatively can filter by fish HS codes after selecting for fish.

# BUNDLE EXPERIMENTATION


```{r}

carp <- fromJSON("data/carp.json")
catfish <- fromJSON("data/catfish.json")
c_mac <- fromJSON("data/chub_mackerel.json")
cod <- fromJSON("data/cod2.json")
herring <- fromJSON("data/herring.json")
lichen <- fromJSON("data/lichen.json")
mac <- fromJSON("data/mackerel.json")
pol <- fromJSON("data/pollock.json")
salmon <- fromJSON("data/salmon.json")
sal_wgl <- fromJSON("data/salmon_wgl.json")
shark <- fromJSON("data/shark.json")
tuna <- fromJSON("data/tuna.json")

```

## Carp
```{r}
carp_nodes <- as_tibble(carp$nodes) %>%
  select(id,shpcountry, rcvcountry) #using select function to reorganise into desired order of columns

carp_edges <- as_tibble(carp$links) %>%
  select(source, target, valueofgoods_omu, weightkg, hscode, arrivaldate)

# rename columns
carp_edges <- carp_edges %>%
  rename('Source' = 'source', 
         'Target' = 'target', 
         'Value_OMU' = 'valueofgoods_omu', 
         'Weight_KG' = 'weightkg', 
         'HS_Code' = 'hscode', 
         'Arrival_Date' = 'arrivaldate')
  
```
## C_mac
```{r}
c_mac_nodes <- as_tibble(c_mac$nodes) %>%
  select(id,shpcountry, rcvcountry) #using select function to reorganise into desired order of columns

c_mac_edges <- as_tibble(c_mac$links) %>%
  select(source, target, valueofgoods_omu, weightkg, hscode, arrivaldate)

# rename columns
c_mac_edges <- c_mac_edges %>%
  rename('Source' = 'source', 
         'Target' = 'target', 
         'Value_OMU' = 'valueofgoods_omu', 
         'Weight_KG' = 'weightkg', 
         'HS_Code' = 'hscode', 
         'Arrival_Date' = 'arrivaldate')
  
```
## Cod
```{r}
cod_nodes <- as_tibble(cod$nodes) %>%
  select(id,shpcountry, rcvcountry) #using select function to reorganise into desired order of columns

cod_edges <- as_tibble(cod$links) %>%
  select(source, target, valueofgoods_omu, weightkg, hscode, arrivaldate)

# rename columns
cod_edges <- cod_edges %>%
  rename('Source' = 'source', 
         'Target' = 'target', 
         'Value_OMU' = 'valueofgoods_omu', 
         'Weight_KG' = 'weightkg', 
         'HS_Code' = 'hscode', 
         'Arrival_Date' = 'arrivaldate')
  
```
## Catfish
Catfish sus, no weight data (underreporting/overreporting is a trait of illegal fishing?)
```{r}
catfish_nodes <- as_tibble(catfish$nodes) %>%
  select(id,shpcountry, rcvcountry) #using select function to reorganise into desired order of columns

catfish_edges <- as_tibble(catfish$links) %>%
  select(source, target, valueofgoods_omu, hscode, arrivaldate)

# rename columns
catfish_edges <- catfish_edges %>%
  rename('Source' = 'source', 
         'Target' = 'target', 
         'Value_OMU' = 'valueofgoods_omu', 
         'HS_Code' = 'hscode', 
         'Arrival_Date' = 'arrivaldate')
  
```
## Herring
```{r}
herring_nodes <- as_tibble(herring$nodes) %>%
  select(id,shpcountry, rcvcountry) #using select function to reorganise into desired order of columns

herring_edges <- as_tibble(herring$links) %>%
  select(source, target, valueofgoods_omu, weightkg, hscode, arrivaldate)

# rename columns
herring_edges <- herring_edges %>%
  rename('Source' = 'source', 
         'Target' = 'target', 
         'Value_OMU' = 'valueofgoods_omu', 
         'Weight_KG' = 'weightkg', 
         'HS_Code' = 'hscode', 
         'Arrival_Date' = 'arrivaldate')
  
```
## Lichen
```{r}
lichen_node <- as_tibble(lichen$nodes) %>%
  select(id,shpcountry, rcvcountry) #using select function to reorganise into desired order of columns

lichen_edges <- as_tibble(lichen$links) %>%
  select(source, target, valueofgoods_omu, weightkg, hscode, arrivaldate)

# rename columns
lichen_edges <- lichen_edges %>%
  rename('Source' = 'source', 
         'Target' = 'target', 
         'Value_OMU' = 'valueofgoods_omu', 
         'Weight_KG' = 'weightkg', 
         'HS_Code' = 'hscode', 
         'Arrival_Date' = 'arrivaldate')
  
```
## Mac
```{r}
mac_nodes <- as_tibble(mac$nodes) %>%
  select(id,shpcountry, rcvcountry) #using select function to reorganise into desired order of columns

mac_edges <- as_tibble(mac$links) %>%
  select(source, target, valueofgoods_omu, hscode, arrivaldate)

# rename columns
mac_edges <- mac_edges %>%
  rename('Source' = 'source', 
         'Target' = 'target', 
         'Value_OMU' = 'valueofgoods_omu', 
         'HS_Code' = 'hscode', 
         'Arrival_Date' = 'arrivaldate')
  
```
## Pollock
```{r}
pol_nodes <- as_tibble(pol$nodes) %>%
  select(id,shpcountry, rcvcountry) #using select function to reorganise into desired order of columns

pol_edges <- as_tibble(pol$links) %>%
  select(source, target, valueofgoods_omu, weightkg, hscode, arrivaldate)

# rename columns
pol_edges <- pol_edges %>%
  rename('Source' = 'source', 
         'Target' = 'target', 
         'Value_OMU' = 'valueofgoods_omu', 
         'Weight_KG' = 'weightkg', 
         'HS_Code' = 'hscode', 
         'Arrival_Date' = 'arrivaldate')
  
```
## Sal WGL
```{r}
sal_wgl_nodes <- as_tibble(sal_wgl$nodes) %>%
  select(id,shpcountry, rcvcountry) #using select function to reorganise into desired order of columns

sal_wgl_edges <- as_tibble(sal_wgl$links) %>%
  select(source, target, valueofgoods_omu, weightkg, hscode, arrivaldate)

# rename columns
sal_wgl_edges <- sal_wgl_edges %>%
  rename('Source' = 'source', 
         'Target' = 'target', 
         'Value_OMU' = 'valueofgoods_omu', 
         'Weight_KG' = 'weightkg', 
         'HS_Code' = 'hscode', 
         'Arrival_Date' = 'arrivaldate')
  
```
## Salmon
```{r}
salmon_nodes <- as_tibble(salmon$nodes) %>%
  select(id,shpcountry, rcvcountry) #using select function to reorganise into desired order of columns

salmon_edges <- as_tibble(salmon$links) %>%
  select(source, target, valueofgoods_omu, weightkg, hscode, arrivaldate)

# rename columns
salmon_edges <- salmon_edges %>%
  rename('Source' = 'source', 
         'Target' = 'target', 
         'Value_OMU' = 'valueofgoods_omu', 
         'Weight_KG' = 'weightkg', 
         'HS_Code' = 'hscode', 
         'Arrival_Date' = 'arrivaldate')
  
```
## Shark
```{r}
shark_nodes <- as_tibble(shark$nodes) %>%
  select(id,shpcountry, rcvcountry) #using select function to reorganise into desired order of columns

shark_edges <- as_tibble(shark$links) %>%
  select(source, target, valueofgoods_omu, weightkg, hscode, arrivaldate)

# rename columns
shark_edges <- shark_edges %>%
  rename('Source' = 'source', 
         'Target' = 'target', 
         'Value_OMU' = 'valueofgoods_omu', 
         'Weight_KG' = 'weightkg', 
         'HS_Code' = 'hscode', 
         'Arrival_Date' = 'arrivaldate')
  
```
## Tuna
```{r}
tuna_nodes <- as_tibble(tuna$nodes) %>%
  select(id,shpcountry, rcvcountry) #using select function to reorganise into desired order of columns

tuna_edges <- as_tibble(tuna$links) %>%
  select(source, target, valueofgoods_omu, hscode, arrivaldate)

# rename columns
tuna_edges <- tuna_edges %>%
  rename('Source' = 'source', 
         'Target' = 'target', 
         'Value_OMU' = 'valueofgoods_omu', 
         'HS_Code' = 'hscode', 
         'Arrival_Date' = 'arrivaldate')
  
```
## Remove Duplicates
```{r}

c_mac_edges <- c_mac_edges %>% distinct()

carp_edges <- carp_edges %>% distinct()

catfish_edges <- catfish_edges %>% distinct()

cod_edges <- cod_edges %>% distinct()

herring_edges <- herring_edges %>% distinct()

lichen_edges <- lichen_edges %>% distinct()

mac_edges <- mac_edges %>% distinct()

pol_edges <- pol_edges %>% distinct()

sal_wgl_edges <- sal_wgl_edges %>% distinct()

salmon_edges <- salmon_edges %>% distinct()

shark_edges <- shark_edges %>% distinct()

tuna_edges <- tuna_edges %>% distinct()

```

```{r}
all_edges<- c("carp_edges", "c_mac_edges", "cod_edges", "catfish_edges", "herring_edges", "lichen_edges", "mac_edges", "pol_edges", "salmon_edges", "sal_wgl_edges", "shark_edges", "tuna_edges")  # Add more dataset names as needed


```

```{r}
unique_hscodes <- character()  # Initialize an empty vector to store unique hs codes

for (all_edges in all_edges) {
  dataset <- get(all_edges)  # Extract the dataset
  
  unique_hscodes <- unique(c(unique_hscodes, dataset$HS_Code))  # Extract unique hs codes and append to the vector
}


```
## Remove all rows with HS_codes irrelevant to bundles
```{r}

filtered_MC2_edges <- MC2_edges[MC2_edges$HS_Code %in% unique_hscodes, ]



```



## Aggregate

```{r}
MC2_edges_aggregated <- filtered_MC2_edges %>%
  group_by(Source,Target) %>%
  summarise(Value_OMU_Total = sum(Value_OMU, na.rm = TRUE),
            Value_USD_Total = sum(Value_USD, na.rm = TRUE),
            Count = n(),
            Average_OMU = mean(Value_OMU, na.rm = TRUE),
            Average_USD = mean(Value_USD, na.rm = TRUE),
            Total_Weight_KG = sum(Weight_KG, na.rm = TRUE),
            Average_Weight_KG = mean(Weight_KG, na.rm = TRUE))


```

## Interactive Graph

```{r}
MC_edges_aggregated2 <- filtered_dataset %>%
  left_join(MC2_nodes, by = c("Source" = "id")) %>%
  left_join(MC2_nodes, by = c("Target" = "id")) %>%
   group_by(Source, Target) %>%
    summarise(Value_OMU_Total = sum(Value_OMU, na.rm = TRUE),
            Value_USD_Total = sum(Value_USD, na.rm = TRUE),
            Count = n(),
            Average_OMU = mean(Value_OMU, na.rm = TRUE),
            Average_USD = mean(Value_USD, na.rm = TRUE)) %>%
  ungroup()
```

```{r}
MC_edges_aggregated2 <- MC_edges_aggregated2 %>%
  rename('from' = 'Source',
         'to' = 'Target')

```

```{r}
still too large
#visNetwork(MC2_nodes, 
           #MC_edges_aggregated2)

```