---
title: "Hands-on_Ex02"
author: "Leonard Lee"
---

# Load Packages

```{r}
pacman::p_load(ggrepel, patchwork,
               ggthemes, hrbrthemes,
               tidyverse)
```

# Import the Data

```{r}

exam_data <- read_csv("data/Exam_data.csv")

```

# Packages and Techniques

## 1: ggrepel

Original Code: ggplot(data=exam_data, aes(x= MATHS, y=ENGLISH)) + geom_point() + geom_smooth(method=lm, size=0.5) +\
geom_label(aes(label = ID), hjust = .5, vjust = -.5) + coord_cartesian(xlim=c(0,100), ylim=c(0,100)) + ggtitle("English scores versus Maths scores for Primary 3")

```{r}
ggplot(data=exam_data, 
       aes(x= MATHS, 
           y=ENGLISH)) +
  geom_point() +
  geom_smooth(method=lm, 
              size=0.5) +  
  geom_label_repel(aes(label = ID), 
                   fontface = "bold") +
  coord_cartesian(xlim=c(0,100),
                  ylim=c(0,100)) +
  ggtitle("English scores versus Maths scores for Primary 3")
```

## 2: ggplot 2 themes

Original Code: ggplot(data=exam_data, aes(x = MATHS)) + geom_histogram(bins=20, boundary = 100, color="grey25", fill="grey90") + theme_gray() + ggtitle("Distribution of Maths scores")

```{r}
ggplot(data=exam_data, 
             aes(x = MATHS)) +
  geom_histogram(bins=20, 
                 boundary = 100,
                 color="grey25", 
                 fill="grey90") +
  ggtitle("Distribution of Maths scores") +
  theme_economist()
```

## 3: hrbrthemes

ggplot(data=exam_data, aes(x = MATHS)) + geom_histogram(bins=20, boundary = 100, color="grey25", fill="grey90") + ggtitle("Distribution of Maths scores") + theme_ipsum()

```{r}
ggplot(data=exam_data, 
             aes(x = MATHS)) +
  geom_histogram(bins=20, 
                 boundary = 100,
                 color="grey25", 
                 fill="grey90") +
  ggtitle("Distribution of Maths scores") +
  theme_ipsum(axis_title_size = 18,
              base_size = 15,
              grid = "Y")
```

## 4: Merging of Graphs

```{r}
p1 <- ggplot(data=exam_data, 
             aes(x = MATHS)) +
  geom_histogram(bins=20, 
                 boundary = 100,
                 color="grey25", 
                 fill="grey90") + 
  coord_cartesian(xlim=c(0,100)) +
  ggtitle("Distribution of Maths scores")
```

```{r}
p2 <- ggplot(data=exam_data, 
             aes(x = ENGLISH)) +
  geom_histogram(bins=20, 
                 boundary = 100,
                 color="grey25", 
                 fill="grey90") +
  coord_cartesian(xlim=c(0,100)) +
  ggtitle("Distribution of English scores")
```

```{r}
p3 <- ggplot(data=exam_data, 
             aes(x= MATHS, 
                 y=ENGLISH)) +
  geom_point() +
  geom_smooth(method=lm, 
              size=0.5) +  
  coord_cartesian(xlim=c(0,100),
                  ylim=c(0,100)) +
  ggtitle("English scores versus Maths scores for Primary 3")
```

## Example of Merging two graphs (p1 and p2)

```{r}
p1 + p2
```

## Merge all three graphs

```{r}
(p1 / p2) | p3
```

## Add Tag

```{r}
((p1 / p2) | p3) + 
  plot_annotation(tag_levels = 'I')
```

## Add insert

```{r}
p3 + inset_element(p2, 
                   left = 0.02, 
                   bottom = 0.7, 
                   right = 0.5, 
                   top = 1)
```

## Composite using patchwork and ggtheme

```{r}
patchwork <- (p1 / p2) | p3
patchwork & theme_economist()
```
